\section{Experience}
\cventry{2018 - Present}{Research Assistant}{Rochester Institute of Technology}{Rochester}{NY}{Fairness in AI, Population level annotator learning for human disagreement prediction\newline{}
Tools used - Python (Scikit-learn, Keras, and TensorFlow), BERT, MongoDB for data storage, and Google Cloud. 
	\begin{itemize}
    \item Led human subjects research through Amazon MTurk and managed a budget of \$10,000. 
	 \item Research to building socially representative and privacy-centric datasets for machine learning pipelines. 
    % \item Working with clustering methods (K-Means and LDA), and supervised learning methods (CNN). 
    % \item Experiments on large datasets (approximately 50,000+) from Reddit, Facebook, YouTube and Twitter.
    \item Research work accepted at EMNLP '23, ACL '23, ICLR '23 Tiny Papers, LREC '22 NLPerspectives, and ECAI '20.
\end{itemize}}

\cventry{2023 May - 2023 August}{Applied Scientist Intern}{Amazon Ads}{New York}{NY}{Project - Contextual Relevancy under weak human-in-the-loop judgments and LLM Assisted Models.\newline{}
Tools used - Python (Scikit-learn and PyTorch), SBERT, MySQL, LLM (LangChain) and AWS. 
\begin{itemize}
    \item Designed methods for understanding annotator quality across different locales and languages. 
    \item Introduced new pipelines for adjusting existing contextual relevancy pipelines to work with annotator scores. 
\end{itemize}}
% \newpage
\cventry{May 2022 - August 2022}{Machine Learning Research Engineer Intern}{Meta formerly known as Facebook}{Menlo Park}{CA}{Facebook Creators Wellbeing Team on Public Conversations.\newline{}
Project - Introduction of a Multi-Label Multi-Task model for assisting page administrations for comment management.\newline{}
Tools used - Python, PHP, and Presto. Python/PyTorch for model building. Presto for data pipelines. 
\begin{itemize}
    \item Collaborations with peers at a team level as well as organization level for adopting existing single level ML models and infrastructure.
    % \item Experimented with real-time data from Facebook users for model building, millions of actions per day. 
    % \item Big data pipelines with Presto (similar to SQL) for collecting and processing data for the model.
    \item The model bypassed the existing individual action-based models used by 40\% based on ROC and PR AUC scores. 
    \item Evaluated the model in production with A/B testing on 4\% of overall global Facebook users. 
\end{itemize}}
\cventry{2018-2022}{Tech/Infrastructure Lead}{LKEMR}{Sri Lanka}{}{ Cloud-based Electronic Medical Record project with the Faculty of Medicine and Colombo North Teaching Hospital.\newline{}Tools used - PHP, SQL, HTML, CSS, and UNIX. Python for data mining. Hosted on DigitalOcean and AWS.
\begin{itemize}
	  \item Web-based electronic patient record management system, tailored for Sri Lanka using PHP backend and MySQL. 
      \item EMR currently holds records for over 1,000 patients across several cities in Sri Lanka.
      \item System is used to identify potential patients with COVID-19, as it is the only EMR widely used in Sri Lanka. 
      \item The work also contributes to open sourced EMR Project, Open-EMR.
\end{itemize}
}
\cventry{January 2021 - July 2021}{Infrastructure Lead for EACL 2021}{European Chapter of the Association for Computational Linguistics}{Virtual}{}{
	    \begin{itemize}
	        \item Built infrastructure for hosting and deploying virtual conference platform on Amazon AWS.
	       % \item Created the pipeline to manage content on AWS using CI/CD.
	        \item Integrated an external registration system with AWS Cognito for single-sign-on (OAuth2) Auth0.
            \item Led a team to manage support requests from Conference chairs, conference sponsors, and attendees.
	       % \item Team Project Planning using Asana.
	    \end{itemize}
}

\cventry{May 2021 - August 2023}{Research Assistant Intern}{Boston College}{Virtual}{}{
Automatic Speech Recognition for low resource languages
\begin{itemize}
    \item Studies on low resource datasets for ASR and their fairness for all speakers.
    \item Advised an REU student preparing for Computer Science and Machine Learning courses.
 \end{itemize}
}

\cventry{May 2019 - August 2019}{Research Assistant}{HEALS Project (part of IBM AI Horizon)}{Troy}{Rensselaer Polytechnic Institute, NY}{Food Data Aggregation, Project to aggregate nutritional information for crowdsourced recipes from FDA\newline{}Collaborative project with the Faculty of Medicine, and Colombo North Teaching Hospital, Sri Lanka.\newline{}Tools used - Python (document processing and SpaCy+doc2vec for NLP).
\begin{itemize}
    \item Research based on natural language processing and information retrieval with the 1M Recipe (1 million) dataset.
    \item Investigated aggregating food-related data sources for the food knowledge graph, used with IBM Watson.
    \item The tool was able to generate the nutritional content per FDA guidelines from a crowdsourced recipe.
 \end{itemize}
}